### 2022-10-12 chapters/conclusion.tex
add : software contributions

\subsection*{Articles}
\begin{enumerate}
      \item \textbf{Taming energy consumption variations in systems benchmarking}: We investigate the phenomenon of variation when measuring the energy consumption of experiments in this study. In this paper, we discuss various hardware and software factors that can amplify variations in recorded energy measures, with a focus on the following research questions:
      \begin{description}
            \item[\textsc{RQ}~1:] Does the benchmarking protocol affect the energy variation?
            \item[\textsc{RQ}~2:] How important is the impact of the processor features on the energy variation?
            \item[\textsc{RQ}~3:] What effect does the operating system have on energy variation?
            \item[\textsc{RQ}~4:] Does the choice of processor make a difference in reducing the energy variation?
      \end{description}

@@

>>>>

\subsection*{Articles}
this part summarizes the contributions that have been already accepted in conferences and journals.

\begin{enumerate}
      \item \textbf{Taming energy consumption variations in systems benchmarking}: We investigate the phenomenon of variation when measuring the energy consumption of experiments in this study. In this paper, we discuss various hardware and software factors that can amplify variations in recorded energy measures, with a focus on the following research questions:
            \begin{description}
                  \item[\textsc{RQ}~1:] Does the benchmarking protocol affect the energy variation?
                  \item[\textsc{RQ}~2:] How important is the impact of the processor features on the energy variation?
                  \item[\textsc{RQ}~3:] What effect does the operating system have on energy variation?
                  \item[\textsc{RQ}~4:] Does the choice of processor make a difference in reducing the energy variation?
            \end{description}

@@

\subsection{Softwares and Tools}
While the benchmarking and optimization parts were presented as chapters in this thesis, the measurement part was primarily based on developing tools that measure the energy consumption for a given use case. The following is a summary of the tools that were developed during this thesis:
\begin{itemize}
      \item \textbf{Jouleit} \url{github.com/powerapi-ng/jouleit}: a tool that can be used to monitor energy consumption for any Linux program, this tool was used to compare the energy consumption of different JVMs.
      \item \textbf{JRefferal} \url{github.com/chakib-belgaid/jreferral}: a tool that allows the user to explore the JVM settings and their impact on the energy consumption of a given Java program. This tool was the result of the second article of this thesis.
      \item \textbf{PyJoules} \url{pypi.org/project/pyJoules}: is a software toolkit to measure the energy footprint of a host machine along the execution of a piece of Python code. It can measure the energy consumption on the level of script, function, and bloc of code.
      \item \textbf{JouleHunter} \url{pypi.org/project/joulehunter}: an energy profiler for python applications. It can be used to highlight the functions that consume the most energy in a given Python program. Its main usage is to help developers do an exploratory analysis of their application to scope the functions that should be optimized to be then targeted by PyJoules.
      \item \textbf{GreenBoard} \url{github.com/chakib-belgaid/greenboard}: A dashboard designed to help developers choose the best stack for their web application. It is based on the results of the third article of the last chapter.

\end{itemize}

\subsection{Future Submissions}
\begin{itemize}
      \item Reducing the energy consumption of Python using non-intrusive techniques
      \item Empirical analysis on the energy consumption of different web frameworks
      \item The impact of programming languages on energy consumption of web services (a case study of RPC protocol)
      \item THow do ORMs affect how much energy is used? A case study of Django and Flask
\end{itemize}
